Subjective Evaluations of Financial Satisfaction and Well-being: A Study of the US General Social Survey

### 2023-03-11 outputs/paper/paper3.qmd
updated future research directions

@@

@@

-   Connect with US census data to check representativeness

-   Connect with other macroeconomic indicators - e.g. inflation, stock markets

>>>>

#### Supplementary Survey

@@

#### Cross-Referencing

Connecting our results with US census data to check for representativeness in respondents answers could strengthen interpretations, and help to understand any discrepancies in self-reported data. This would also help us understand how the new methodology implemented by the GSS in 2021 may have influenced self-reported results.

Bringing in other macroeconomic indicators, such as inflation and capital market trends, can also provide an extra dimension to understanding how wealth has evolved and been impacted over time.

@@
